Analysis

### 2022-01-07 code/R/Analysis.Rmd
NARS04 QC

NARS17_p1 = d5 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NARS-13 Parameter combination") +
  facet_wrap(vars(as.factor(maxDist))) +
  scale_color_gradient(low="blue", high="red")

NARS17_p2 = d5 %>% 
  arrange(mm, ascending = T) %>% 
  filter(mm == 0) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm)) + 
  ggtitle("THUL-01 All zero mismatches") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

@@

>>>>

NARS17_p1 = d5 %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm, colour = mm)) + 
  ggtitle("NARS-17 Parameter combination") +
  facet_wrap(vars(as.factor(maxDist))) +
  scale_color_gradient(low="blue", high="red")

NARS17_p2 = d5 %>% 
  arrange(mm, ascending = T) %>% 
  filter(mm == 0) %>% 
  ggplot() +
  geom_point(aes(x=runMean, y = maxDisap, size = mm)) + 
  ggtitle("NARS-17 All zero mismatches") +
  facet_wrap(vars(maxDist))+scale_color_gradient(low="blue", high="red")

@@

```{r}
tempNARS04 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/tempNARS04.csv")

tempNARS04 %>% 
  filter(x_c > 1100 & x_c < 1110) %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, colour = as.factor(objectID))) + 
  xlim(1100,1110) + 
  ylim(2250,2320)

tempNARS04 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, colour = as.factor(objectID)), size = 0.5)
